---
title: "Weekend Homework - Clustering"
output: html_document
---


# Clustering weekend homework

```{r}
library(tidyverse)
library(janitor)
library(fastDummies)
library(broom)
library(rpart)
library(rpart.plot)
library(factoextra)
```

```{r}
customers <- read_csv("data/mall_customers.csv") %>%
  clean_names()
```

You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings.

We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers.

Perform k-means clustering and chose a value of k.
```{r}
selected_customers <- customers %>%
  select(annual_income_k, spending_score_1_100)
```
```{r}
customers_scaling <- selected_customers %>%
  mutate_all(scale)

summary(customers_scaling)
```
```{r}
fviz_nbclust(customers_scaling, kmeans, method = "wss", nstart = 25)
```
```{r}
fviz_nbclust(customers_scaling, kmeans, method = "gap_stat")
```
```{r}
fviz_nbclust(customers_scaling, kmeans, method = "silhouette", nstart = 25)
```
a k of 5 generally seems to be the optimal choice.

Visualise the clustering for your chosen value of k.
```{r}
clustered_customers <- kmeans(customers_scaling, 5, nstart = 25)

clustered_customers
```
```{r}
clustered_customers$size
```
```{r}
clusters <- augment(clustered_customers, customers)

ggplot(clusters, aes(annual_income_k, spending_score_1_100, colour = .cluster)) +
  geom_point()
```


Do you think the clustering seems a good fit for this data?

Visually it appears that k-means clustering is a good fit for this data. visually after scaling the data it does appear to have 5 distinct clusters. When choosing the k value too, there were two methods that indicated that 5 was a cluster value that had significance. 

Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the ‘Segmentation & clustering intro’ lesson).

The 4th .cluster (or the light blue cluster) was a cluster that had a low annual income and also had a low spending score. 

