---
title: "Homework week 10 day 04"
output: html_notebook
---

# 1 MVP

variables: 
id - Unique ID for each home sold
date - Date of the home sale
price - Price of each home sold
bedrooms - Number of bedrooms
bathrooms - Number of bathrooms, where .5 accounts for a room with a toilet but no shower
sqft_living - Square footage of the apartments interior living space
sqft_lot - Square footage of the land space
floors - Number of floors
waterfront - A dummy variable for whether the apartment was overlooking the waterfront or not
view - An index from 0 to 4 of how good the view of the property was
condition - An index from 1 to 5 on the condition of the apartment,
grade - An index from 1 to 13, where 1-3 falls short of building construction and design, 7 has an average level of construction and design, and 11-13 have a high quality level of construction and design.
sqft_above - The square footage of the interior housing space that is above ground level
sqft_basement - The square footage of the interior housing space that is below ground level
yr_built - The year the house was initially built
yr_renovated - The year of the house’s last renovation
zipcode - What zipcode area the house is in
lat - Lattitude
long - Longitude
sqft_living15 - The square footage of interior housing living space for the nearest 15 neighbors
sqft_lot15 - The square footage of the land lots of the nearest 15 neighbors
```{r}
library(tidyverse)
```
```{r}
house <- read_csv("data/kc_house_data.csv")
```

You might like to think about removing some or all of date, id, sqft_living15, sqft_lot15 and zipcode (lat and long provide a better measure of location in any event).
```{r}
removed_house <- house %>%
  select(-c(date, id, sqft_living15, sqft_lot15, zipcode))
```

Have a think about how to treat waterfront. Should we convert its type?
```{r}
unique(removed_house$waterfront)
```

We converted yr_renovated into a renovated logical variable, indicating whether the property had ever been renovated. You may wish to do the same.
```{r}
removed_house %>%
  mutate(yr_renovated = as.integer(as.logical(yr_renovated)))
```

Have a think about how to treat condition and grade? Are they interval or categorical ordinal data types?
```{r}
library(fastDummies)
```
```{r}
dummy_house <- removed_house %>%
  dummy_cols(select_columns = "condition", remove_first_dummy = TRUE, remove_selected_columns = TRUE) %>%
  mutate(short = ifelse(grade <= 3, 1, 0)) %>%
  mutate(average = ifelse(grade <= 10 & grade > 3, 1, 0)) %>%
  mutate(high = ifelse(grade <= 13 & grade > 10, 1, 0)) %>%
  select(-grade)

dummy_house
```


Check for aliased variables using the alias() function (this takes in a formula object and a data set). [Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. Remove variables that lead to an alias. Check the ‘Elements of multiple regression’ lesson for a dropdown containing further information on finding aliased variables in a dataset.
```{r}
# Alias is useful to check if we have aliased variables, i.e. one or more
# variables that can be computed from other variables
alias(price ~ ., data = dummy_house)
```
```{r}
# seems that sqft_basement can be computed from sqft_living - sqft_above.
# let's drop sqft_living leaving just the two contributions sqft_basement and 
# sqft_above
dummy_house <- dummy_house %>%
  select(-"sqft_living")

glimpse(dummy_house)
```


Systematically build a regression model containing up to four main effects (remember, a main effect is just a single predictor with coefficient), testing the regression diagnostics as you go

splitting datasets into numeric and non-numeric columns might help ggpairs() run in manageable time, although you will need to add either a price or resid column to the non-numeric dataframe in order to see its correlations with the non-numeric predictors.

```{r}

```

