---
title: "inmates"
output: html_notebook
---

```{r}
library(tidyverse)
library(dplyr)
library(stringr)
library(readr)
```



```{r}
inmates <- read.table(file = 'data/inmates.tsv', sep = '\t', header = TRUE)
```

```{r}
str(inmates)
```


# 4 Recoding excercise

1. Change the ‘M’/‘F’ values in gender to be ‘Male’/‘Female’.

```{r}
inmates %>%
  mutate(gender = recode(gender, 
                         "M" = "Male",
                         "F" = "Female")
         )
```


2. For the race variable, everything is in capital letters, change each level to title case. Also combine ‘AMER IND’ and ‘ASIAN’ into an ‘Other’ category.

```{r}
inmates$race = str_to_title(inmates$race)
inmates

inmates %>%
  mutate(race = recode(race, 
                         "Amer Ind" = "Other",
                         "Asian" = "Other")
         )

```


3a. Make a new variable bond_level which is High whenever the bond for an inmate is above $1,000,000 and Normal otherwise.

```{r}
bond_level_inmates <- inmates %>%
  mutate(bond_level = recode(bond_amount,
                             '1000000' = "High",
                             '2000' = "Normal"))
```


3b. How many inmates have a high bond level?

```{r}

```


5. Modify the detainer variable so that NONE, IMIGRATION and FEDERAL are in title case and all other levels are set to Other.

```{r}
unique(inmates[c("detainer")])
```
```{r}
inmates$detainer = str_to_title(inmates$detainer)

inmates %>%
  mutate(detainer = recode(detainer,
                           "Other State" = "Other",
                           "Special Parole" = "Other",
                           "State Of Ct" = "Other",
                           "Do Not Release" = "Other"))
```

