---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```


```{r}
tweets <- read_csv("data/code_clan_tweets.csv")
```


# 3 MVP

1. Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
dim(tweets)
names(tweets)
```

2. Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
no_na <- tweets %>%
  mutate(is_quote = na_if(is_quote, TRUE)) %>%
  drop_na(is_quote)

favourite_count <- sum(no_na$favorite_count)

favourite_count
```


3. Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
retweet_count <- tweets %>%
  group_by(source) %>%
  mutate(is_quote = na_if(is_quote, TRUE)) %>%
  drop_na(is_quote) %>%
  summarise(mean_retweets = mean(retweet_count))
retweet_count
```


4. Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
tweets %>%
  summarise()
```


5. Find the mean number of characters that a CodeClan tweet contains.


```{r}
tweets %>%
  summarise(avg_tweet_length = mean(display_text_width))

  
```


6. The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
code_clan_info <- read_csv("data/code_clan_info.csv")
```

```{r}
tweet_info <- left_join(tweets, code_clan_info, "tweet_id")
```


7. From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.

```{r}
codeclan_hashtags <- tweet_info %>%
  mutate(hashtags_lower = str_to_lower(hashtags)) %>%
  select(tweet_id, hashtags_lower) %>%
  na.omit

codeclan_hashtags
```

