---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(janitor)
library(tidyverse)
```

```{r}
items <- read_csv("data/20190928-items.csv") %>%
  clean_names()
```

```{r}
items
```


Find the brand with the highest numbers of phones in the dataset.

```{r}
items %>%
  group_by(brand) %>%
  count(brand) %>%
  arrange(desc(n))
```


For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?

```{r}
items <- items %>%
  filter(brand == "Samsung") %>%
  mutate(prob = 1 / n())
items
```

```{r}
items %>%
  ggplot(aes(x = rating, y = prob)) +
  geom_col() + 
  xlab("Ratings") + 
  ylab("Probabiltiy")
```

```{r}
items_stat <- items %>%
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
items_stat
```

```{r}
items %>%
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = items_stat$mean,
      sd = items_stat$sd
    ),
    col = "red"
  )
```




We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

```{r}

```

