---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
meteorite_landings <- read_csv("data/meteorite_landings.csv")
```

# 1.1 The .R file

* 1. Read the data into R

```{r}
str(meteorite_landings)
```

```{r}
head(meteorite_landings, 20)
```

* 2. Change the names of the variables to follow our naming standards.

```{r}
renamed_meteorite <- meteorite_landings %>%
  rename(
    meteorite_id = id,
    meteorite_name = name,
    mass_in_grams = 'mass (g)',
    geo_location = GeoLocation
  )
```

* 3. Split in column GeoLocation into latitude and longitude, the new latitude and longitude columns should be numeric.

```{r}
meteorite_wider <- renamed_meteorite %>%
  separate(geo_location, c("latitude", "longitude"), sep = ",")

head(meteorite_wider)
```

```{r}
remove_meteorite <- meteorite_wider %>%
  mutate(latitude = str_remove_all(latitude, "\\(")) %>%
  mutate(longitude = str_remove_all(longitude, "\\)"))

remove_meteorite
  
```


* 4. Replace any missing values in latitude and longitude with zeros.

```{r}
zero_meteorite <- remove_meteorite %>%
  replace_na(list(latitude = 0, longitude = 0))
zero_meteorite
```

* 5. Remove meteorites less than 1000g in weight from the data.

```{r}
thousand_meteorite <- zero_meteorite %>%
  filter(mass_in_grams > 1000)
thousand_meteorite
```

* 6. Order the data by the year of discovery.

```{r}
ordered_meteorite <- thousand_meteorite %>%
  arrange(desc(year))

ordered_meteorite
```

# data range check.

* The data has the variable names we expect (“id”, “name”, “mass (g)”, “fall”, “year”, “GeoLocation”).

* Latitude and longitude are valid values. (Latitude between -90 and 90, longitude between -180 and 180)

```{r}
numeric_meteorite <- ordered_meteorite %>%
  transform(latitude = as.numeric(latitude),
            longitude = as.numeric(longitude))
```

```{r}
filtered_meteorite <- numeric_meteorite %>%
  filter(latitude >= -90) %>%
  filter(latitude <= 90) %>%
  filter(longitude >= -180) %>%
  filter(longitude <= 180)
```

# 1.2 The .Rmd file 

* 1. Read the cleaned data into R.

```{r}
filtered_meteorite
```


* 2. Find the names and years found for the 10 largest meteorites in the data.

```{r}
top_ten_meteorites <- filtered_meteorite %>%
  slice_max(mass_in_grams, n = 10) %>%
  select(meteorite_name, mass_in_grams, year)

top_ten_meteorites
```


* 3. Find the average mass of meteorites that were recorded falling, vs. those which were just found.

```{r}
avg_meteorite <- filtered_meteorite %>%
  group_by(fall) %>%
  summarise(avg_meteorite_size = mean(mass_in_grams))

avg_meteorite
```


* 4. Find the number of meteorites in each year, for every year since 2000.

```{r}
yearly_meteorite <- filtered_meteorite %>%
  group_by(year) %>%
  filter(year > 2000) %>%
  tally() %>%
  arrange(desc(n))

yearly_meteorite

```



