---
title: "R Notebook"
output: html_notebook
---

```{r}
library(janitor)
library(tidyverse)
```

# 1 MVP

Load the data again, clean_names(), and re-familiarise yourself with it
```{r}
ames <- read_csv("data/ames.csv") %>%
  clean_names()
```

Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?
```{r}
ames %>%
  ggplot(aes(x = lot_area)) + 
  geom_histogram(col = "white", fill = "steel blue", alpha = 0.7)
```

Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
library(infer)
```

```{r}
sample_100 <- ames %>%
  rep_sample_n(size = 100, reps = 1)
sample_100
```

```{r}
infer_resample <- sample_100 %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")
infer_resample
```
```{r}
infer_ci_95 <- infer_resample %>%
  get_confidence_interval(level = 0.95, type = "percentile")

infer_ci_95
```


Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution
```{r}
infer_resample %>%
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = infer_ci_95)
```

You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?
```{r}
infer_ci_99 <- infer_resample %>%
  get_confidence_interval(level = 0.99, type = "percentile")

infer_ci_99
```

```{r}
infer_resample %>%
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = infer_ci_99)
```
Calculate the point estimate of the mean(lot_area)
```{r}
infer_resample %>%
  summarise(mean(stat))
```

