---
title: "backpack"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
backpack
```

* Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
dim(backpack)
```
```{r}
colnames(backpack)
```


* Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_bar()
```


* Question 3.

Are there differences in backpack weight between sex?

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, fill = sex) +
  geom_bar()
```

Answer: from this graph there isnt much difference in the backpack weight between the sex.

* Question 4.

What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack) +
  aes(x = body_weight, y = backpack_weight) +
  geom_point()
```

Answer: generally the heavier the body_weight the heavier the backpack_weight

* Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, y = body_weight, colour = sex) +
  geom_point()
```
Answer: Males generally weight more but backpack_weight is fairly even. 


* Question 6.

What proportion of students report back pain?

```{r}
ggplot(backpack) +
  aes(x = back_problems) +
  geom_histogram() +
  coord_flip()
```
Answer: around 1/3 of students reported back problems.

* Question 7.

Is this proportion different between men and women?

```{r}
ggplot(backpack) +
  aes(x = back_problems, fill = sex) +
  geom_histogram() +
  coord_flip()
```
Answer: A far higher % of Females reported to have vack problems, almost 1/2. Whereas Males were only around 1/4.5. 

* Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, fill = sex) +
  geom_dotplot() +
  facet_grid(back_problems ~ sex, labeller = 
               "label_both")
```


```{r}
ggplot(backpack) +
  aes(x = body_weight, fill = sex) +
  geom_dotplot() +
  facet_grid(back_problems ~ sex, labeller = 
               "label_both")
```
Answer: there isnt too much correlation between backpack_weight and 
