---
title: "week06_day01_homework"
output: html_notebook
---

```{r}
library(janitor)
library(prob)
library(gtools)
library(tidyverse)
```

```{r}
titanic <- read_csv("data/titanic.csv")
titanic
```

```{r}
unique(titanic$class)
```
```{r}
crew <- c("engineering crew", "victualling crew", "restaurant staff", "deck crew")
passangers <- c("1st", "2nd", "3rd")

reworked_titanic <- titanic %>%
  mutate(
    class = if_else(class %in% crew, "crew", class),
    class = if_else(class %in% passangers, "passanger", class)
  ) 

    
unique(reworked_titanic$class)
```

```{r}
table <- reworked_titanic %>%
  tabyl(class, survived)

table <- table %>%
  adorn_totals(where = c("row", "col")) %>%
  adorn_percentages(denominator = "all") %>%
  adorn_title()

table
```

```{r}
reworked_titanic$did_survive <- reworked_titanic$survived == "yes"

titanic
```

```{r}
prob_of_surviving <- reworked_titanic %>%
  filter(did_survive == TRUE) %>%
  summarise(prob = n() / nrow(reworked_titanic))

prob_of_surviving
```

```{r}
prob_survive_given_crew <- reworked_titanic %>%
  filter(class == "crew") %>%
  summarise(prob = sum(did_survive)/n())
prob_survive_given_crew
```

```{r}
prob_survive_given_crew <- reworked_titanic %>%
  filter(class == "passanger") %>%
  summarise(prob = sum(did_survive)/n())
prob_survive_given_crew
```

1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
s_die <- rolldie(1)
s_die
```
```{r}
s_die_rolls_less_than_five <- s_die %>%
  filter(X1 < 5)%>%
  summarise(prob = n() / nrow(s_die))
s_die_rolls_less_than_five
```


2. How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
s_three_die <- rolldie(3) %>%
  summarise(size_of_s = n())
s_three_die
```


3. In an experiment where we roll four dice:

i. how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?

```{r}
s_four_dice <- rolldie(4) 
s_four_dice
```
```{r}
s_four_dice_with_count <- s_four_dice %>%
  mutate(roll_count = X1 + X2 + X3 + X4) 

s_four_dice_with_count %>%
  filter(roll_count > 4, roll_count < 8) %>%
  nrow()
```

ii. what is the probability of this event?

```{r}
s_four_dice_with_count %>%
  filter(roll_count > 4, roll_count < 8) %>%
  summarise(prob = n() / nrow(s_four_dice_with_count))
```


iii. what assumptions do we apply in answering part ii?

The assumption being made is that all factors in the creation of the data are fair. (aka, all four dice are fair rolls)


4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

```{r}
five_folks <- c("Amy, 1", "James, 2", "Carl, 3", "Jamie, 4", "Kerry, 5")

five_folks <- as.tibble(
  permutations(
    n = 5,
    r = 4,
    v = five_folks,
    repeats.allowed = FALSE
  )
)

five_folks
```

4 times it will occur

4/3/2/1   5/4/3/2   5/3/2/1   5/4/2/1 