---
title: "homework_week05_day02"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
qb_revenue_breakdown
qb_monthly_sales
qb_competitors
qb_device_data
```
# 4.1 Part 1

1. Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.
```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

ggplot(qb_revenue_breakdown) +
  aes(x = Year, y = Revenue, fill = Product) +
  theme_light() +
  labs(x = "Year", y = "Revenue (£)") +
  scale_fill_manual(values = col_scheme) +
  geom_col() 
```


2. Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year. This data is inside qb_monthly_sales, but you will need to use subset.
```{r}
flagship_product <- qb_monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales")
  
ggplot(flagship_product) +
  aes(x = Date, y = Amount) +
  theme_light() +
  labs(x = "Date", y = "Money in (£)", title = "Kwikbit Unit 1 Sales") +
  geom_line() +
  geom_point()
  
```


3. Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
cost_and_revenue <- qb_monthly_sales %>% 
  filter(Cashflow != "Kwikbit Unit 1 Sales")

ggplot(cost_and_revenue) +
  aes(x = Date, y = Amount, colour = Cashflow) +
  scale_colour_manual(values = c("#E89FE9", "#BD7040")) +
  theme_light() +
  labs(x = "Date", y = "Money in (£)", title = "Total Revenue / Cost") +
  geom_line() +
  geom_point()
```


4. Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}
ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, fill = Company) +
  scale_fill_manual(values = col_scheme) +
  theme_light() +
  geom_area() 
  
```


5. Now show the sales from the 5 competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, colour = Company) +
  scale_colour_manual(values = col_scheme) +
  theme_light() +
  labs(x = "Year", y = "Revenue in (£)", title = "Company Revenues") +
  geom_line() +
  geom_point()
```


6. Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between individuals and people. Data is in qb_device_data.

```{r}
qb_device_data <- 
mutate(qb_device_data, decimal_hour = hours + (mins/60))

ggplot(qb_device_data) +
  aes(x = decimal_hour, y = counts, colour = device) +
  geom_line() + 
  scale_x_continuous("Time (hours)") +
  scale_y_continuous("Steps") +
  facet_grid(id ~ device) +
  scale_colour_manual(values = col_scheme) +
  theme_light() +
  ggtitle("Comparison between KwikBit Unit1 and Competitors for 5 individuals")
  
```






