---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

* MVP

*** Load the data into a dataframe project

```{r}
pro_man <- read_csv("data/project_management.csv")
```



```{r}
pro_man
```

explanitory variables -> independent variables -> for this example estimated_length
single outcome -> dependent variables -> for this example actual_length

*** Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.
```{r}
pro_man %>%
  ggplot() +
  aes(x = estimated_length, y = actual_length) +
  geom_point()
```

*** Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain.


*** Perform a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable. Save the model object to a variable.
```{r}
model <- lm(formula = estimated_length ~ actual_length, data = pro_man)
model
```
```{r}
fitted(model)
```


*** Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?

```{r}
library(modelr)
```

```{r}
pro_man <- pro_man %>%
  add_predictions(model) %>%
  add_residuals(model)
pro_man
```
```{r}
pro_man %>%
  ggplot(aes(x = estimated_length)) +
  geom_point(aes(y = actual_length)) +
  geom_line(aes(y = pred), col = "red")
```
```{r}
pro_man %>%
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_abline(
    intercept = model$coefficients[1],
    slope = model$coefficients[2],
    col = "red"
  )
```


*** Is the relationship statistically significant? Remember, to assess this you need to check the p-value of the regression coefficient (or slope/gradient). But you should first check the regression diagnostic plots to see if the p-value will be reliable (don’t worry about any outlier points you see in the diagnostic plots, we’ll return to them in the extension).
